---
title: "Extended Data Figure 8: Cluster distributions across tissues"
author: "David Zemmour"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r doc-code, include=FALSE}
source("../code/R/doc_code.R")
```

This figure is produced by
[`script/FigureS8.R`](https://github.com/dzemmour/immgenT-cosmo-analysis/blob/main/script/FigureS8.R).
The code below is shown for reference (not re-executed on this page); the
images are its pre-rendered output.

## Code {#figs8}

It is the same plot as [Figure 6a](Figure6.html#fig6a), drawn for the five
organs that figure leaves out. Both organ lists and the plotting code live in
[`code/R/organ_mde.R`](https://github.com/dzemmour/immgenT-cosmo-analysis/blob/main/code/R/organ_mde.R).

```{r figs8-code, code=code_for("../script/FigureS8.R", "^"), eval=FALSE}
```

```{r figs8-img, echo=FALSE, out.width="32%"}
knitr::include_graphics(c(
  "assets/ExtendedDataFigure8/S8_MDE_baseline_submandibulargland.png",
  "assets/ExtendedDataFigure8/S8_MDE_baseline_uterus.png",
  "assets/ExtendedDataFigure8/S8_MDE_baseline_peritonealcavity.png",
  "assets/ExtendedDataFigure8/S8_MDE_baseline_placenta.png",
  "assets/ExtendedDataFigure8/S8_MDE_baseline_bonemarrow.png"))
```

::: {.figcaption}
**Extended Data Fig. 8.** All-T MDE showing the distribution of T cells at
baseline in submandibular gland, uterus, peritoneal cavity, placenta and bone
marrow, coloured by lineage.
:::
